The paper on \Large \bf Blockchain Frontrunning

### 2018-09-04 frontrunning/Latex/setup/table.tex
[frontrunning] fix table shortstack

\multirow{9}{*}{Games, CryptoCollectibles \\ (ERC 721)}		& \textbf{CryptoKitties (3)} \\  
												& Ethermon(4)\\
												& Cryptogirl (9)\\
												& Gods Unchained TCG (12)\\
												& Blockchain Cuties(15)\\
												& ETH.TOWN! (16)\\
												& 0xUniverse (18)\\
												& MLBCrypto Baseball (19)\\
												& HyperDragons(25)\\ \hline

>>>>

\multirow{9}{*}{\shortstack{Games \\ CryptoCollectibles \\ (ERC 721)}}		& \textbf{CryptoKitties (3)} \\  
												& Ethermon(4)\\
												& Cryptogirl (9)\\
												& Gods Unchained TCG (12)\\
												& Blockchain Cuties(15)\\
												& ETH.TOWN! (16)\\
												& 0xUniverse (18)\\
												& MLBCrypto Baseball (19)\\
												& HyperDragons(25)\\ \hline
